A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform

### 2020-06-30 paperMIC2020/paperIEEE-MIC2020-V1.tex

\section{Dynamic target tracking and problem setting} 
\todo[inline]{Needs to reviewed}
 \label{sec:problemSetup}

Suppose that a wheeled mobile robot (follower) with coordinate $(x,y)$ and orientation $\theta\in[-\pi,\pi)~\si{\radian}$ with respect to the global X-Y coordinate has a linear speed $\nu$ and steering angle $\gamma$ which are considered as the two control actions. Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$. The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[d]})^T=[x_k^{[d]},y_k^{[d]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time. Note that this trajectory is completley random. The target motion is modeled by the following discrete-time system:
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
 \end{align}  
with $\mathbf{u}_k^{[\ell]}\in\mathbb{R}^2$ being the control inputs of the target movment. 
\\ The follower robot is to maintain a constant safe-distance $d>0$ from target. The dynamic car-like model of the follower robot is defined as follows:
  \begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
    }
   \caption{Mobile robot and its dynamic target tracking problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     x_{k+1}& =x_{k}+T_s\nu_{k}\cos{(\theta_{k}+\gamma_{k})} + \zeta_1,\\  
     y_{k+1}& =y_{k}+T_s\nu_{k}\sin{(\theta_{k}+\gamma_{k})}+ \zeta_2,\\
     \theta_{k+1}&=\theta_{k}+T_s\nu_{k}\frac{\sin{(\gamma_{k})}}{l}+ \zeta_3,
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 \\
\hl{Note that the follower dynamic model obeys Ackermann steering principle where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the front wheel steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi),$ $\nu_k$ is the linear speed, $l$ is the distance between the drive wheels of the robot, and $\zeta_1,\zeta_2,\zeta_3\in\mathbb{R}$ are the model uncertainties.} 
\\
We then define the error vector as:
 \begin{multline}
     \label{eq:stateError}
   \mathbf {e}_k^T = [\rho_e,\theta_e]^T =
   [\sqrt{x_e^2+y_e^2},\theta_e]^T = \\
   \begin{bmatrix}
     \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
     (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
     \theta_k^{'} - \theta_k
   \end{bmatrix},
 \end{multline}

@@

 \section{Computer Experiments and Results}
 \label{sec:resultsExperiments}
 This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using the Pioneer 3-DX in CoppeliaSim. The results obtained by the authors in \hl{cite flairs paper here} are validated using the commercial robot simulator, CoppeliaSim as a prelminary step to implement the Algorithm experimantally in real world. we present the dynamics of the tracking error and the convergence characterisitcs of the actor and critic weights. The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ % 
  \[Q=0.001 
  \begin{bmatrix}
  1       & 0   \\
  0       & 1   \\
  \end{bmatrix},
  R=0.00001
  \begin{bmatrix}
  1       & 0 \\
  0       & 1 
  \end{bmatrix}.\]
 The actor and critic learning rates $\ell_c$ are set to  $0.01$ and $0.0001$. The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.
 The CoppeliaSim simulator accuratly mimic what would happen in a realworld scenario following idustry standatrds and guidlines. The Pioneer robot model and the  was initally placed at position (-1,-2.5) m.The Target modeled as a cylinder was initially positioned on a random position around the origin (0,0). The simulation was run for 
\begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
`     }
   \caption{CoppeliaSim Scene.}
   \label{fig:CoppeliaSim Scene}
 \end{figure}

 \begin{figure*}[htbp]%
 \subfigure[][]{%
    \label{fig:trajectoryRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
	\subfigure[][]{%    
    \label{fig:euclideanDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
\subfigure[][]{%
    \label{fig:stateErrorRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:controlInputsRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:weightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
     \subfigure[][]{%
    \label{fig:actorWeightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
  \label{fig:peformanceRandomTrajectory}%
\end{figure*}

% \textit{In the sequel, computer experiments  are conducted to validate the performance of the proposed model-free adaptive learning algorithm in real-time. The results of computer experiments highlight the dynamics of the tracking errors and the convergence characteristics of the proposed algorithm (i.e., updating the critic weights). This will judge the ability of the follower robot to track independent motion trajectory of the leader robot under two different independent leader-motion trajectories. The computer experiments are realized using MATLAB simulation environment. The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.01,0.01,0.005]$ and $\mathbf{R} = \mathrm{diag}[10^{-6}, 10^{-6}].$ % 
%  \[Q=0.001 
%  \begin{bmatrix}
%  10       & 0   & 0\\
%  0       & 10   & 0\\
%  0       & 0   &5 \\
%  \end{bmatrix},
%  R=0.000001
%  \begin{bmatrix}
%  1       & 0 \\
%  0       & 1 
%  \end{bmatrix}.\]
% The learning rate $\ell_c$ is set to  $0.0001$. The sampling time $T_s$ is set to $0.08 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.
%
%% In the first s\begin{figure*}[htbp]%
%\centering
%\parbox[c]{0.48\textwidth}{\centering Parallel parking}
%\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%\\
%%\begin{align*}
%% $\dot x^{[\ell]}(t) = \nu^{[\ell]}(t)\cos\theta^{[\ell]}(t),$ %
%% $\dot y^{[\ell]}(t) = \nu^{[\ell]}(t)\sin\theta^{[\ell]}(t).$
%% \dot\theta^\ell(t) &= \omega(t),
%%\end{align*}
% Initially, the leader's position is set to be the same for a short period of time with $\nu^{\ell} = 0 , \gamma^{\ell} = 0$. Then it starts to move on a horizontal line with $\nu^{\ell} = 0.1 $ [m/s], eventually the leader starts to move on an inclined path with $\nu^{\ell} = 0.2$ [m/s], $\gamma^{\ell} = 45\degree$. The leader is initially placed at $(x,y) = (5, 2)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree $, while the follower  is initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0\degree$. Note that during this scenario, the critic weights converge rapidly and the tracking errors decay till the follower tracks the leader. The trajectory phase plan plot, tracking error states, control signals, and tuning of critic weights are shown in Fig.~\ref{fig:performanceRectilinearTrajectory}. %
%% \begin{figure*}[htbp]%
%%     \centering
%%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
%%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%%     \\
%%     \subfigure[][]{%
%%         \label{fig:trajectoryRectilinearDistance}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/trajectoryRectlinearDistance} }
%%     \subfigure[][]{%
%%         \label{fig:stateErrorRectilinearDistance}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/stateErrorRectlinearDistance} }
%%     \\
%%     \subfigure[][]{%
%%         \label{fig:controlInputsRectilinearDistance}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/controlInputRectlinearDistance} }
%%     \subfigure[][]{%
%%         \label{fig:weightRectilinearDistance}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/weightRectilinearDistance} }
%%     \caption[Leader-follower performance for rectilinear trajectory.]{First scenario (rectilinear trajectory): 
%%         \subref{fig:trajectoryRectilinearDistance} leader-follower trajectories,~\subref{fig:stateErrorRectilinearDistance} state tracking errors,~\subref{fig:controlInputsRectilinearDistance} linear speed and steering angle of the follower, and    \subref{fig:weightRectilinearDistance} critic weights.}%
%%     \label{fig:performanceRectilinearTrajectory}%
%% \end{figure*}
% A relatively unplanned complex trajectory-tracking scenario is considered. The leader moves according to a sinusoidal trajectory so that %
%%  \begin{align*}
%% $x^{[\ell]}(t) = \alpha (t) \in [0,10\pi],$ %
%% $y^{[\ell]}(t) = 5 \,\sin(\alpha t),$ and %
%% $\theta^{[\ell]}(t) = cos(\alpha t).$  %
%%        \end{align*}
%% 
% The leader robot  was initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree$ while the follower robot was initially placed at a random position around $(x,y) = (0, 0)~\si{[\meter]}$ with a random orientation. The simulation results are summarized in Figure~\ref{fig:performanceSinewaveTrajectory}. It is observed that the critic weights take more time to converge compared to the earlier scenario,  which is reluctant to the complexity of the independent trajectory of the leader. This result emphasizes the adaptability of the proposed adaptive learning mechanism to different scenarios. Further, the follower starts to move away from the leader at the beginning of the simulation before it finally converges to the leader where the tracking errors are bounded by a safe distance $d.$ % 
%% \begin{figure*}[htbp]%
%%     \centering
%%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
%%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%%     \\
%%     \subfigure[][]{%
%%         \label{fig:trajectorySinewave}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/trajectorySinewaveDistance} }
%%     \subfigure[][]{%
%%         \label{fig:stateErrorSinewave}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/stateErrorSinewaveDistance} }
%%     \\
%%     \subfigure[][]{%
%%         \label{fig:controlInputSinewave}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/controlInputSinewaveDistance} }
%%     \subfigure[][]{%
%%         \label{fig:weightSinewaveDistance}%
%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/weightSinewaveDistance} }
%%     \caption[Leader-follower performance for nonlinear trajectory.]{Second scenario (sinusoidal trajectory): 
%%         \subref{fig:trajectorySinewave} leader-follower trajectories,~\subref{fig:stateErrorSinewave} state tracking errors,~\subref{fig:controlInputSinewave} linear speed and steering angle of the follower, and    \subref{fig:weightSinewaveDistance} critic weights.}%
%%     \label{fig:performanceSinewaveTrajectory}%
%% \end{figure*}
%\textit{In the third case study we rely on completley random path for the leader robot to evaluate the effectivenss of the proposed algorithm as a solution for the leader follower tracking problem. The leader is to follow a random path defined by the model described in (2), with $\gamma$ being a random value, The follwer is to maitain an offset distance of $d = 0.5 $ [m]. Note that the path of the leader is not pre defined and the algorithm being completlety model free. The results are summerized in Fig. \ref{fig:peformanceRandomTrajectory}. }

%The results are summarized in Fig.~\ref{fig:peformanceRandomTrajectory}. %
%
%\begin{figure*}[htbp]%
%\centering
%\parbox[c]{0.48\textwidth}{\centering Parallel parking}
%\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%\\
%\subfigure[][]{%
%    \label{fig:trajectoryRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/trajectorySinewave} }
%\subfigure[][]{%
%    \label{fig:stateErrorRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/stateErrorSinewave} }
%\\
% \subfigure[][]{%
%    \label{fig:controlInputsRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/controlInputSinewave} }
% \subfigure[][]{%
%    \label{fig:weightRandomDistance}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/weightRectilinearDistance} }
%\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
%  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
%  \label{fig:peformanceRandomTrajectory}%
%\end{figure*}

 \section{Conclusion} \label{sec:conclusion}

% A novel policy iteration mechanism based on a model-free reinforcement learning approach is presented for solving a conventional leader-follower formation problem using car-like mobile robots. The proposed approach does not rely on model parameters inherent in the mobile robots employed in this work. The follower robot is able to follow the leader robot that navigates along unplanned trajectories of various complexities while maintaining a nonzero safe distance between them. To the best of authors' knowledge, this is the first milestone of its kind where a model-free policy iteration based reinforcement learning approach is employed in a multi-robot formation control problem. The future work is going  to extend the learning algorithm for solving a time-varying formation control problem using networked robots.

% \section*{Acknowledgment}

% The preferred spelling of the word ``acknowledgment'' in America is without 
 an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
 G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
 acknowledgments in the unnumbered footnote on the first page.

 \bibliographystyle{IEEEtran}
 \bibliography{bib/refsSuruzWeb,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP}
% \bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
\end{document}

>>>>

\section{Dynamic target tracking and problem setting} 
\todo[inline]{review}
 \label{sec:problemSetup}

Suppose that a wheeled mobile robot (follower) with coordinate $(x,y)$ and orientation $\theta\in[-\pi,\pi)~\si{\radian}$ with respect to the global X-Y coordinate has a linear speed $\nu$ and steering angle $\gamma$ which are considered as the two control actions. Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$. The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[d]})^T=[x_k^{[d]},y_k^{[d]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time. Note that this trajectory is completley random. The target motion is modeled by the following discrete-time system:
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
 \end{align}  
with $\mathbf{u}_k^{[\ell]}\in\mathbb{R}^2$ being the control inputs of the target movment. 
\\ The follower robot is to maintain a constant safe-distance $d>0$ from target. The dynamic car-like model of the follower robot is defined as follows:
  \begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
    }
   \caption{Mobile robot and its dynamic target tracking problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
   	 	\nu_{k}(t) = \frac{1}{l}(\nu_{R,k} + \nu_{l,k}),\\ 
   	 	\omega_{k}(t)=\frac{\nu_{k}(t)}{l}tan(\gamma(t)) 	
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 \\
where $\omega(t)$ and $\nu_k(t)$ is the angular and linear velocity, $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi)$ ,$l$ is the distance between the drive wheels of the robot.
\\
We then define the error vector as:
 \begin{multline}
     \label{eq:stateError}
   \mathbf {e}_k^T = [\rho_e,\theta_e]^T =
   [\sqrt{x_e^2+y_e^2},\theta_e]^T = \\
   \begin{bmatrix}
     \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
     (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
     \theta_k^{'} - \theta_k
   \end{bmatrix},
 \end{multline}

@@

 \section{Computer Experiments and Results}
 \label{sec:resultsExperiments}
 \todo[inline]{review}
 This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using the Pioneer 3-DX  robot. The proposed Actor-Critic RL algorithm is tested using the commercial robot simulator CoppeliaSim in integration with Matlab software as a prelminary step to implement the Algorithm experimantally in real world.Here we present the performance of the proposed method and the convergence characterisitcs of the actor and critic weights. The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ % 
  \[Q=0.001 
  \begin{bmatrix}
  1       & 0   \\
  0       & 1   \\
  \end{bmatrix},
  R=0.00001
  \begin{bmatrix}
  1       & 0 \\
  0       & 1 
  \end{bmatrix}.\]

 The actor and critic learning rates $\ell_c$,$\ell_a$ are set to  $0.0001$ and $0.01$ respectively. The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.2$ [m].

  During the simulation CoppeliaSim simulator accuratly mimics what would happen in a realworld scenario following idustry standatrds and guidlines.The setup of the virtual expirement is illustrated  in figure \ref{fig:CoppeliaSim Scene} where pioneer robot model was initally placed at position $(x,y) = (-1,-2.5) $ [m] with an orientation $\theta = 0 \degree$ .The Target which is modeled as a cylinder object was initially located at a random position around  $(x,y) = (0,0)$ [m]. The simulation was run for the duration of 15 seconds. 
  The Target is set to move on a completely random trajectory starting from a random position. We intensify that the follower robot has no previous knoweledge of the dynamic model of the moving target nor it's initial position. The results obtained by the simulation are shown in figure \ref{fig:simulationResults}. the control actions of the pioneer robot are determined by the random actor weights .we clearly see tracking error converges to the desired value of $d$ = 0.2 [m] along with control signal converging to values that allows target tracking. the results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's path in an online manner.      
\begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
`     }
   \caption{Simulation Setup}
   \label{fig:CoppeliaSim Scene}
 \end{figure}

 \begin{figure*}[htbp]%

 \subfigure[][]{%
    \label{fig:trajectoryRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
	\subfigure[][]{%    
    \label{fig:euclideanDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
\subfigure[][]{%
    \label{fig:stateErrorRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:controlInputsRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:weightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
     \subfigure[][]{%
    \label{fig:actorWeightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
  \label{fig:peformanceRandomTrajectory}%
	\label{fig:simulationResults}
\end{figure*}

 \section{Conclusion} \label{sec:conclusion}
	\todo[inline]{review}
	A model free actor-critic reinfoncement learning algorithm for dynamic target tracking has been validated using virtual robot experimantation platform where a differenitial drive mobile robot and a randomly moving target are utilized in the simulation.Opposed to previous approaches in the litrature this Algorithm possess the advantage of being completlety model free and doesn't rely on any dynamic model to be known in priori. The actor weights which drives the control actions of the robot sucessfully converge to values that enable the robot to track the moving target through unplanned trajectory. To the authors knowlege this work is the first of its kind to employ a model-free actor-critic RL approach  in the context of dynamic target tracking. In future work the proposed approach will be applied to multi-robot scenarios where a number of robots are to achieve a certain task in unknown enviroments.

 \bibliographystyle{IEEEtran}
 \bibliography{bib/refsSuruzWeb,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP}
\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
\end{document}
